Debiased Calibration for Generalized Two-Phase Sampling

### 2024-05-04 final/reports/prelim_paper.tex
Updated prelim_paper to include fixed simulation study for topic 1.

    \textcolor{red}{You should include an intercept in $\bf x_i$. }
    \textcolor{blue}{I have been including an intercept, but I forgot to add it
    into these notes.}
  \item[3.] Debiased Calibration with Population Constraints (DC-Pop): This 
    solves

@@

  \item[4.] Debiased Calibration with Estimated Population Constraints (DC-Est):
    This solves Equation~\eqref{eq:primal} with $q_i = 1$.
\end{itemize}

@@

\begin{table}[ht!]
  \centering
  \begin{tabular}{lcc}
    \toprule
    Estimator & Estimated Variance & Notes \\
    \midrule
    $\pi^*$ 
    & {\scriptsize$\left(\frac{1}{n_1} - \frac{1}{N}\right) \hat s^2_Y + 
      \sum\limits_{i \in A_2} \frac{w_{1i}^2}{N^2} 
        \frac{(1 - \pi_{2i|1})}{\pi_{2i|1}^2}y_i^2$}
    & {\scriptsize$\hat s^2_Y = \frac{1}{n_2 - 1}\sum\limits_{i \in A_2} (y_i -
    \bar y_i)^2$} \\
    TP-Reg  
    & {\scriptsize$\left(\frac{1}{n_1} - \frac{1}{N}\right) \hat s^2_\eta + 
      \sum\limits_{i \in A_2} \frac{w_{1i}}{N^2} 
        \frac{(1 - \pi_{2i|1})}{\pi_{2i|1}^2}\varepsilon_i^2$}
    & {\scriptsize$ \eta_i = \bf x_i'\bm \beta + \delta_{2i} w_{2i|1}\varepsilon_i,\;
        \varepsilon_i = (y_i - \bf x_i' \bm \beta)$} \\
    DC-Pop  
    & {\scriptsize$\left(\frac{1}{n_1} - \frac{1}{N}\right) \hat s^2_\varepsilon + 
      \sum\limits_{i \in A_2} \frac{w_{1i}}{N^2} 
        \frac{(1 - \pi_{2i|1})}{\pi_{2i|1}^2}\varepsilon_i^2$}
    & {\scriptsize$\eta_i = \bf z_i' \bm \phi + \delta_{2i}w_{2i|1}\varepsilon_i,\;
        \varepsilon_i = (y_i - \bf z_i'\bm \phi)$} \\
    DC-Est  
    & {\scriptsize$\left(\frac{1}{n_1} - \frac{1}{N}\right) \hat s^2_\eta + 
      \sum\limits_{i \in A_2} \frac{w_{1i}}{N^2} 
        \frac{(1 - \pi_{2i|1})}{\pi_{2i|1}^2}\varepsilon_i^2$}
    & {\scriptsize$\eta_i = \bf z_i' \bm \phi + \delta_{2i}w_{2i|1}\varepsilon_i,\;
        \varepsilon_i = (y_i - \bf z_i' \bm \phi)$} \\
    \bottomrule
  \end{tabular}
  \caption{This table gives the formulas for each variance estimator used in
  Simulation 1. For the derivation of the estimated variance of the DC-Pop
estimatator see Appendix A.}
  \label{tab:varforms}
\end{table}

\textcolor{red}{I am not sure about the variance estimation formula in Table 1. 
They are different from what we discussed before. I wonder whether you can make
the sampling rate $n/N$ negligible so that the second term becomes
insignificant. How about making $N=50,000$, $n_1=500$, and $n_2=200$?}

\textcolor{blue}{The result with $N = 50,000$, $n_1 = 500$ and $E[n_2] \approx
200$}

\begin{table}[ht!]
  \centering
  {\color{blue}\input{tables/tpdcsim50000_mean.tex}}
% This table was generated from ../../src/explore/proto-dctpmcmc.R
  \caption{\textcolor{blue}{This table shows the results of Simulation Study 1 with
      a different finite population and Phase 2 selection probability.
      It displays the Bias, RMSE, empirical 95\% confidence interval, and a
      t-statistic assessing the unbiasedness of each estimator for the
      estimators: $\pi^*$, TP-Reg, DC-Pop, and DC-Est.}}
\end{table}

@@

\textcolor{red}{Dr. Kim is this confidence interval good enough? It seems
slightly high for me.}

>>>>

    %\textcolor{red}{You should include an intercept in $\bf x_i$. }
    %\textcolor{blue}{I have been including an intercept, but I forgot to add it
    %into these notes.}
  \item[3.] Debiased Calibration with Population Constraints (DC-Pop): This 
    solves

@@

  \item[4.] Debiased Calibration with Estimated Population Constraints (DC-Est):
    This solves Equation~\eqref{eq:primal} with $q_i = 1$.
  \item[5.] Linearized Debiased Calibration with Population Constraints (Eta-Pop):
    This is the linearized estimate DC-Pop using the linearization in
    Theorem~\ref{thm:dc1}.
  \item[6.] Linearized Debiased Calibration with Estimated Population
    Constraints (Eta-Est): This is the linearized estimate DC-Est using the
    linearization in Theorem~\ref{thm:dc1}.
\end{itemize}

@@

\begin{table}[ht!]
  \centering
  \begin{tabular}{lcc}
    \toprule
    Estimator & Estimated Variance & Notes \\
    \midrule
    $\pi^*$ 
    & {\scriptsize$\left(\frac{1}{n_1} - \frac{1}{N}\right) \hat s^2_Y + 
      \sum\limits_{i \in A_2} \frac{w_{1i}^2}{N^2} 
        \frac{(1 - \pi_{2i|1})}{\pi_{2i|1}^2}y_i^2$}
    & {\scriptsize$\hat s^2_Y = \frac{1}{n_2 - 1}\sum\limits_{i \in A_2} (y_i -
    \bar y_i)^2$} \\
    TP-Reg  
    & {\scriptsize$\left(\frac{1}{n_1} - \frac{1}{N}\right) \hat s^2_\eta + 
      \sum\limits_{i \in A_2} \frac{w_{1i}}{N^2} 
        \frac{(1 - \pi_{2i|1})}{\pi_{2i|1}^2}\varepsilon_i^2$}
    & {\scriptsize$ \eta_i = \bf x_i'\bm \beta + \delta_{2i} w_{2i|1}\varepsilon_i,\;
        \varepsilon_i = (y_i - \bf x_i' \bm \beta)$} \\
    DC-Pop  
    & {\scriptsize$\left(\frac{1}{n_1} - \frac{1}{N}\right) \hat s^2_\varepsilon + 
      \sum\limits_{i \in A_2} \frac{w_{1i}}{N^2} 
        \frac{(1 - \pi_{2i|1})}{\pi_{2i|1}^2}\varepsilon_i^2$}
    & {\scriptsize$\eta_i = \bf z_i' \bm \phi + \delta_{2i}w_{2i|1}\varepsilon_i,\;
        \varepsilon_i = (y_i - \bf z_i'\bm \phi)$} \\
    DC-Est  
    & {\scriptsize$\left(\frac{1}{n_1} - \frac{1}{N}\right) \hat s^2_\eta + 
      \sum\limits_{i \in A_2} \frac{w_{1i}}{N^2} 
        \frac{(1 - \pi_{2i|1})}{\pi_{2i|1}^2}\varepsilon_i^2$}
    & {\scriptsize$\eta_i = \bf z_i' \bm \phi + \delta_{2i}w_{2i|1}\varepsilon_i,\;
        \varepsilon_i = (y_i - \bf z_i' \bm \phi)$} \\
    Eta-Pop & Same as DC-Pop & \\
    Eta-Est & Same as DC-Est & \\
    \bottomrule
  \end{tabular}
  \caption{This table gives the formulas for each variance estimator used in
  Simulation 1. For the derivation of the estimated variance of the DC-Pop
estimatator see Appendix A.}
  \label{tab:varforms}
\end{table}

%\textcolor{red}{I am not sure about the variance estimation formula in Table 1. 
%They are different from what we discussed before. I wonder whether you can make
%the sampling rate $n/N$ negligible so that the second term becomes
%insignificant. How about making $N=50,000$, $n_1=500$, and $n_2=200$?}
%
%\textcolor{blue}{The result with $N = 50,000$, $n_1 = 500$ and $E[n_2] \approx
%200$}
%
%\begin{table}[ht!]
%  \centering
%  {\color{blue}\input{tables/tpdcsim50000_mean.tex}}
%% This table was generated from ../../src/explore/proto-dctpmcmc.R
%  \caption{\textcolor{blue}{This table shows the results of Simulation Study 1 with
%      a different finite population and Phase 2 selection probability.
%      It displays the Bias, RMSE, empirical 95\% confidence interval, and a
%      t-statistic assessing the unbiasedness of each estimator for the
%      estimators: $\pi^*$, TP-Reg, DC-Pop, and DC-Est.}}
%\end{table}

@@

\textcolor{red}{While DC-Est still does not outperform TP-Reg, it is equivalent
to Eta-Est, which is a regression estimator.}

\textcolor{red}{The variance estimates look good now. I needed to think of
DC-Pop as a regression estimator instead of a two-phase regression estimator.}
